How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-14 docs/PhysicsPaper/StokesErosion.tex
NM

%-----------------------------------------------------------------------------------------------%
\section{\edit{Numerical methods}}
%\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:numerics}
%-----------------------------------------------------------------------------------------------%
\edit{To investigate the large-scale features of microscopic erosion, we
require numerical methods that are accurate in both space and time.
Section~\ref{sec:bie} reformulates the governing equations using a
boundary integral equation that is discretized with a spectrally
accurate quadrature rule, and Section~\ref{sec:int_evo} describes our
second-order numerical method for evolving the bodies. We note that the
numerical methods described in both sections require that the geometry
is two-dimensional. Extending our work to three dimensions requires
entirely different time quadrature formulas and time stepping methods.}

>>>>

%-----------------------------------------------------------------------------------------------%
\section{\edit{Numerical methods}}
%\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:numerics}
%-----------------------------------------------------------------------------------------------%
\edit{To investigate the large-scale features of microscopic erosion, we
require numerical methods that are accurate in both space and time.
Section~\ref{sec:bie} reformulates the governing equations using a
boundary integral equation that is discretized with a spectrally
accurate quadrature rule, and Section~\ref{sec:int_evo} describes our
second-order numerical method for evolving the bodies. We note that the
numerical methods described in both sections require the geometry
to be two-dimensional. Extending our work to three dimensions would require
 different quadrature formulas and time-stepping methods.}
